Tabular Constraint Learning

### 2016-04-14 Paper/ECAI/tabular.tex
updating the formalization

\section{Formalization}
\tias{More gentle}
\samuel{Explain concepts on example}
\sergey{subgroup notation, rework the solution definition}
\subsection{Groups, Type-consistency and Constraints}
In this work we distinguish the following types of data: numeric and textual. The numeric type has two subtypes: integers and floats. We also consider the special element called \textit{None}, which has two types: numeric and textual. A set is called \textit{type-consistent} iff all elements are either numeric or textual. Certain constraints, such as \textit{rank} or \textit{series}, make use of the numeric sub-types by requiring its arguments to be integers.

>>>>

\section{Formalization}
\samuel{Explain concepts on example}
\sergey{subgroup notation, rework the solution definition}
\subsection{Groups, Type-consistency and Constraints}
In this work we focus on the spreadsheet data, which is physically one big table, but conceptually consists of multiple tables, see Fig \ref{fig:main_example} for an example. Formally, a table is $n \times m$ matrix, each entry is called a \textit{cell}. A cell has a type, e.g. namely numeric. In this work we distinguish the two types of data: numeric and textual. The numeric type has two subtypes: integers and floats. We also consider the special element called \textit{None}, which has two types: numeric and textual.

Based on these types we introduce a notation of type consistency for a set of elements. A set is called \textit{type-consistent} iff all elements are either numeric or textual. Certain constraints, such as \textit{rank} or \textit{series}, make use of the numeric sub-types by requiring its arguments to be integers.

We use the notation $T[a,b]$ to refer to a particular cell in the table $T$ at the row with index $a$ and the column with index $b$. To refer to the $a$-th row (column) we use the following syntax $T[a,{:}]$ ($T[{:},a]$), to refer to a subrange from $a$ to $b$ we use $T[a{:}b,]$ ($T[,a{:}b]$).
